### 2020-11-10 thesis/appendix_1.tex
start addressing comment 46

%\begin{landscape}
\begin{longtable}[c]{|p{5cm}|p{11cm}|}
%\centering
\caption{Description of the 5 umbrella species (adapted from \cite{rayfield_priorisation_2018}).}
\label{tab:species} \\
%\begin{tabular}{|p{5cm}|p{10cm}|}
\hline
\hline
\textbf{Species} & \textbf{Description} \\ \hline
Northern short-tailed Shrew \newline \textit{Blarina brevicauda} & Abundant small fossorial mammal. This highly active species can live in a diversity of habitats (grasslands, old fields, marshy areas, gardens, and some developed areas) but is mainly found in deciduous and mixed old forests with thick understories that provide good cover for hiding from predators. It feeds primarily on earthworms found in areas with moist soils. It has a high reproductive rate and is generally a poor disperser although it can cross gaps of 50-100m. \\ \hline
American marten \newline \textit{Martes americana} & Small vagile carnivorous predator. Found in core areas of dense (\textgreater{}60\% cover) and old (\textgreater{}70 yr) coniferous or mixed forests with complex vertical and horizontal structure. It requires large home ranges (above hundreds of ha). It generally avoids large openings and clearings (above a few hundred meters wide) but crosses roads and frozen rivers easily. Deep persistent snow pack is a habitat critical element as it excludes predators (Canis latrans) and competitors (Martes pennanti) and provides good hunting conditions. This forest specialist is particularly sensitive to human activities. Juveniles are able to cover tens of kilometers when dispersing, more than what would be expected from body mass-based estimates. Trapped for its fur, this species has patrimonial and economical importance. \\ \hline
Red-Backed Salamander \newline \textit{Plethodon cinereus} & Terrestrial salamander. This sedentary and territorial forest-dwelling species lives under the leaf litter or coarse woody debris in mature and moist deciduous and mixed forests. It is a poor disperser that uses tens of square meters as a home range and rarely ventures more than 50 m in open fields. Roads and edges (up to 20-30 m) have a negative effect on populations’ densities and reduce individual movements. \\ \hline
Wood Frog \newline \textit{Rana sylvatica} & Forest-specialist amphibian. This species prefers mixed and coniferous stands with closed canopy (\textgreater 40\%) and moist soil covered with woody debris (for egg deposition) but can adapt to other closed habitats. Both aquatic (palustrine, fish-free wetlands, not open and permanent ones) and terrestrial habitats are essential, and distance between both should not exceed ca. 600 m. It is sensitive to forest edge (25-35 m), gaps, high intensity agriculture, human developments and recent clearcuts that can act as barriers to movement. This poor disperser is particularly sensitive to roads and habitat loss (fidelity to the first breeding pond). \\ \hline
Black Bear \newline \textit{Ursus americanus} & Large opportunistic omnivorous mammal. This species likes deciduous and mixed mature forest with dense cover interspersed with small clearings and early-successional stages of forest that are rich in berry production (depends on main soil surface deposit). It uses broad territories (tens to hundreds of square km) to follow the fruiting season by going upslope with the season. It is an effective seed disperser because it can travel long distances (up to 390 km), in particular male juveniles. It clearly avoids human activity (up to 5 km) and roads (up to 800 m), in particular highways, and is likely to take a detour instead of crossing a 60 m gap. \\
\hline
\hline
%\end{tabular}
\end{longtable}
%\end{landscape}

>>>>

% %\begin{landscape}
% \begin{longtable}[c]{|p{5cm}|p{11cm}|}
% %\centering
% \caption{Description of the 5 umbrella species (adapted from \cite{rayfield_priorisation_2018}).}
% \label{tab:species} \\
% %\begin{tabular}{|p{5cm}|p{10cm}|}
% \hline
% \hline
% \textbf{Species} & \textbf{Description} \\ \hline
% Northern short-tailed Shrew \newline \textit{Blarina brevicauda} & Abundant small fossorial mammal. This highly active species can live in a diversity of habitats (grasslands, old fields, marshy areas, gardens, and some developed areas) but is mainly found in deciduous and mixed old forests with thick understories that provide good cover for hiding from predators. It feeds primarily on earthworms found in areas with moist soils. It has a high reproductive rate and is generally a poor disperser although it can cross gaps of 50-100m. \\ \hline
% American marten \newline \textit{Martes americana} & Small vagile carnivorous predator. Found in core areas of dense (\textgreater{}60\% cover) and old (\textgreater{}70 yr) coniferous or mixed forests with complex vertical and horizontal structure. It requires large home ranges (above hundreds of ha). It generally avoids large openings and clearings (above a few hundred meters wide) but crosses roads and frozen rivers easily. Deep persistent snow pack is a habitat critical element as it excludes predators (Canis latrans) and competitors (Martes pennanti) and provides good hunting conditions. This forest specialist is particularly sensitive to human activities. Juveniles are able to cover tens of kilometers when dispersing, more than what would be expected from body mass-based estimates. Trapped for its fur, this species has patrimonial and economical importance. \\ \hline
% Red-Backed Salamander \newline \textit{Plethodon cinereus} & Terrestrial salamander. This sedentary and territorial forest-dwelling species lives under the leaf litter or coarse woody debris in mature and moist deciduous and mixed forests. It is a poor disperser that uses tens of square meters as a home range and rarely ventures more than 50 m in open fields. Roads and edges (up to 20-30 m) have a negative effect on populations’ densities and reduce individual movements. \\ \hline
% Wood Frog \newline \textit{Rana sylvatica} & Forest-specialist amphibian. This species prefers mixed and coniferous stands with closed canopy (\textgreater 40\%) and moist soil covered with woody debris (for egg deposition) but can adapt to other closed habitats. Both aquatic (palustrine, fish-free wetlands, not open and permanent ones) and terrestrial habitats are essential, and distance between both should not exceed ca. 600 m. It is sensitive to forest edge (25-35 m), gaps, high intensity agriculture, human developments and recent clearcuts that can act as barriers to movement. This poor disperser is particularly sensitive to roads and habitat loss (fidelity to the first breeding pond). \\ \hline
% Black Bear \newline \textit{Ursus americanus} & Large opportunistic omnivorous mammal. This species likes deciduous and mixed mature forest with dense cover interspersed with small clearings and early-successional stages of forest that are rich in berry production (depends on main soil surface deposit). It uses broad territories (tens to hundreds of square km) to follow the fruiting season by going upslope with the season. It is an effective seed disperser because it can travel long distances (up to 390 km), in particular male juveniles. It clearly avoids human activity (up to 5 km) and roads (up to 800 m), in particular highways, and is likely to take a detour instead of crossing a 60 m gap. \\
% \hline
% \hline
% %\end{tabular}
% \end{longtable}
% %\end{landscape}

### 2020-11-10 thesis/chap_1.tex
start addressing comment 46

Connectivity modeling is similar to land use change modeling inasmuch as the diversity of methods at the researcher’s disposal is large \citep{calabrese_comparison_2004}. As mentioned in the intro, we implemented an analysis of Potential Functional Connectivity, or PFC. A typical PFC modeling workflow can be broken down to 3 steps: species selection, Habitat suitability modeling and connectivity analysis. The three steps are described below, and the methodology partially follows the methodology of Rayfield et al. This part of the methods is summarized in figure \ref{fig:workflow2}.\\

@@

Species selection is unchanged from Rayfield et al. The five species chosen are presented in the appendix table \ref{tab:species}. It was demonstrated that modeling the connectivity needs of those 5 species was equivalent to modeling the needs of 14 species in the study region \citep{meurant_selecting_2018, albert_applying_2017}\\

@@

Habitat suitability analysis consists in reclassifying land use data into a resistance surface which is then used to model connectivity. For each of the maps obtained from the land use change analysis (for each of the timestep in every iteration and for each of the 5 species), we followed the following steps to reclass land use into resistance:
\begin{enumerate}
\item Classify the landscape as \textbf{forest} and \textbf{non forest}.
\item Reclassify non-forest pixels into resistance following the supplementary tables in  \citeauthor{rayfield_priorisation_2018}, with only a few alterations. See table \ref{tab:key_non_forest} for the reclassification key.
\item Clump the forest landscape into contiguous \textbf{patches} using queen case neighborhood (includes diagonal).
\item Reclassify pixels in all patches as suitable (value = 1) unsuitable (value = 0) or moderately suitable (value = 0.5), based on forest age and type, and following guidelines in the supplementary tables in  \citeauthor{rayfield_priorisation_2018}.  The key for such reclassification is recorded in table \ref{tab:suit_pixls}.
\item  Compute the mean patch value based on the clumped outputs.
\item Classify each patch as \textbf{possibly suitable} or \textbf{unsuitable}, with a cut-off value of 0.5.
\item Among the suitable patches, calculate their size.
\item Classify \textbf{possibly suitable} patches into \textbf{fully suitable} patches or \textbf{too small} patches based on their size, using the values provided by \citeauthor{rayfield_priorisation_2018} (see table \ref{tab:patch_size}).
\item Reclassify patches into resistance, once again following the guidelines in \citeauthor{rayfield_priorisation_2018}'s supplementary tables. See table \ref{tab:hab_or_not} for the reclassification key.
\item Patch the re-classified non-forest map with the re-classified patches map. 
\end{enumerate}

>>>>

Connectivity modeling is similar to land use change modeling inasmuch as the diversity of methods at the researcher’s disposal is large \citep{calabrese_comparison_2004}. As mentioned in the intro, we implemented an analysis of Potential Functional Connectivity, or PFC. A typical PFC modeling workflow can be broken down to 3 steps: species selection, Habitat suitability modeling and connectivity analysis. The three steps are described below, and the methodology partially follows the methodology of \cite{rayfield_priorisation_2018}. This part of the methods is summarized in figure \ref{fig:workflow2}.\\

@@

The species selection process is unchanged from \cite{rayfield_priorisation_2018}. The species are the Northern short-tailed Shrew (\textit{Blarina brevicauda}), the American marten (\textit{Martes americana}), the Red-Backed Salamander (\textit{Plethodon cinereus}), the Wood Frog (\textit{Rana sylvatica}), and the Black Bear (\textit{Ursus americanus}). As previusly mentionned, these  species are considered umbrella species from the standpoint of ecological connectivity, as it has been shown that modeling the connectivity needs of those 5 species was equivalent to modeling the needs of 14 species in the study region \citep{meurant_selecting_2018, albert_applying_2017}\\

@@

Habitat suitability analysis consists in reclassifying land use data into a resistance surface which is then used to model connectivity. For each of the maps obtained from the land use change analysis (for each of the timestep in every iteration and for each of the 5 species), we followed the following steps to reclass land use into resistance:
\begin{enumerate}
\item Classify the landscape as \textbf{forest} and \textbf{non forest}.
\item Reclassify non-forest pixels into resistance following the supplementary tables in  \cite{rayfield_priorisation_2018}, with only a few alterations. See table \ref{tab:key_non_forest} for the reclassification key.
\item Clump the forest landscape into contiguous \textbf{patches} using queen case neighborhood (includes diagonal).
\item Reclassify pixels in all patches as suitable (value = 1) unsuitable (value = 0) or moderately suitable (value = 0.5), based on forest age and type, and following guidelines in the supplementary tables in  \citeauthor{rayfield_priorisation_2018}.  The key for such reclassification is recorded in table \ref{tab:suit_pixls}.
\item  Compute the mean patch value based on the clumped outputs.
\item Classify each patch as \textbf{possibly suitable} or \textbf{unsuitable}, with a cut-off value of 0.5.
\item Among the suitable patches, calculate their size.
\item Classify \textbf{possibly suitable} patches into \textbf{fully suitable} patches or \textbf{too small} patches based on their size, using the values provided by \citeauthor{rayfield_priorisation_2018} (see table \ref{tab:patch_size}).
\item Reclassify patches into resistance, once again following the guidelines in \citeauthor{rayfield_priorisation_2018}'s supplementary tables. See table \ref{tab:hab_or_not} for the reclassification key.
\item Patch the re-classified non-forest map with the re-classified patches map. 
\end{enumerate}
